First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-05-20 paper/paper.tex
paper: Reworded some of the motivation, added TODO citations for last two Elliott papers (which both use homomorphic specification)

%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan,screen]{acmart}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{stmaryrd}
\usepackage{amsmath}

@@

@@

\section{Introduction}

@@

A major benefit of the Haskell language is that you can often derive an
implementation from a specification, either partially or fully. When it is not
possible to fully derive an implementation from a specification, it is often
easier to check an implementation against a specification, due in part to the
management of side effects in Haskell. This is more difficult to do in
imperative languages like C or CUDA (as they provide no restrictions on where
side effects can occur).

Using Haskell EDSLs that allow the use of powerful language features like
pattern matching, these advantages can be brought to other domains where it is
currently either difficult or impossible to use Haskell.

\begin{todo}
  Cite examples. Conal Elliott's last two papers (the one about convolutions and
  the latest one about automatic differentiation), would probably be good
  examples of this in Haskell.

  A paper which describes a Haskell implementation of a specification given as
  an operational semantics would also be a good example.
\end{todo}

>>>>

%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan,screen]{acmart}
\usepackage[switch]{lineno}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{stmaryrd}
\usepackage{amsmath}

@@

% \renewcommand{\linenumberfont}{\color{blue}}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{red}}

@@

\linenumbers
\section{Introduction}

@@

A major benefit of the Haskell language is that it is frequently possible derive
a Haskell implementation from a specification, either partially or fully. When
it is not possible to fully derive an implementation from a specification, it is
often easier to check a Haskell implementation against a specification than it
is in many imperative languages due, in part, to the management of side effects
in Haskell. This is more difficult to do using an imperative language such as C,
as they provide no restrictions on where side effects can occur.

Haskell EDSLs that support powerful language features like pattern matching
allow these advantages to be brought to problem domains where it is currently
either difficult or impossible to use a language that has these benefits.

\begin{todo}
  Cite examples where Haskell implementations have been derived specifications.
  Conal Elliott's latest two papers (as of May 2020),
  \cite{Elliott-2018-ad-icfp} and \cite{Elliott2019-convolution-extended}, would
  be good examples of this.

  A paper which describes a Haskell implementation derived from an operational
  semantics would also be a good example.
\end{todo}
